---
title: "Stat535_HW4"
author: "Jie Wang"
date: "October 10, 2017"
output: pdf_document
---

Read the data:
```{r}
rm(list=ls())
dat <- read.csv("Rgraphics/dataSets/EconomistData.csv")
head(dat)
```

#Exercise I:

1. Create a scatter plot with CPI on the x axis and HDI on the y axis:
```{r}
library(ggplot2)
ggplot(dat, aes(x = CPI, y = HDI)) + geom_point()
```

2. Color the points blue:
```{r}
ggplot(dat, aes(x = CPI, y = HDI)) + geom_point(color="blue")
```

3. Map the color of the the points to Region:
```{r}
ggplot(dat, aes(x = CPI, y = HDI)) + geom_point(aes(color=Region))
```

4. Make the points bigger by setting size to 2:
```{r}
ggplot(dat, aes(x = CPI, y = HDI)) + geom_point(aes(color=Region), size=2)
```

5. Map the size of the points to HDI.Rank:
```{r}
ggplot(dat, aes(x = CPI, y = HDI)) + geom_point(aes(color=Region, size=HDI.Rank))
```

#Exercise II:

1. Re-create a scatter plot with CPI on the x axis and HDI on the y axis (as you did in the previous exercise):
```{r}
ggplot(dat, aes(x = CPI, y = HDI)) + geom_point()
```

2. Overlay a smoothing line on top of the scatter plot using geom_smooth:
```{r}
ggplot(dat, aes(x = CPI, y = HDI)) + geom_point()+geom_smooth()
```

3. Overlay a smoothing line on top of the scatter plot using geom_smooth, but use a linear model for the predictions. Hint: see ?stat_smooth:
```{r}
ggplot(dat, aes(x = CPI, y = HDI)) + geom_point()+geom_smooth(method="lm")
```

4. Overlay a smoothing line on top of the scatter plot using geom_line. Hint: change the statistical transformation.
```{r}
ggplot(dat, aes(x = CPI, y = HDI))+geom_point()+geom_line(stat = "smooth", method = "loess")
```

5. BONUS: Overlay a smoothing line on top of the scatter plot using the default loess method, but make it less smooth. Hint: see ?loess.
```{r}
ggplot(dat, aes(x = CPI, y = HDI)) +geom_point() +geom_smooth(span = .3)
```

#Exercise III

1. Create a scatter plot with CPI on the x axis and HDI on the y axis. Color the points to indicate region.
```{r}
pc1 <- ggplot(dat, aes(x = CPI, y = HDI, color = Region)) +geom_point()
pc1
```

2. Modify the x, y, and color scales so that they have more easily-understood names (e.g., spell out “Human development Index” instead of “HDI”).
```{r}
dat$Region <- factor(dat$Region,
                     levels = c("EU W. Europe",
                                "Americas",
                                "Asia Pacific",
                                "East EU Cemt Asia",
                                "MENA",
                                "SSA"),
                     labels = c("OECD",
                                "Americas",
                                "Asia &\nOceania",
                                "Central &\nEastern Europe",
                                "Middle East &\nnorth Africa",
                                "Sub-Saharan\nAfrica"))
pc2 <- ggplot(dat, aes(x = CPI, y = HDI, color = Region)) +geom_point()+
scale_x_continuous(name = "Corruption Perceptions Index, 2011 (10=least corrupt)",
                       limits = c(.9, 10.5),
                       breaks = 1:10) +
scale_y_continuous(name = "Human Development Index, 2011 (1=Best)",
                       limits = c(0.2, 1.0),
                       breaks = seq(0.2, 1.0, by = 0.1))
pc2
```

3. Modify the color scale to use specific values of your choosing. Hint: see ?scale_color_manual.
```{r}
pc3 <- pc2 + scale_color_manual(name = "Region of the world",
                       values = c("#24576D",
                                  "#099DD7",
                                  "#28AADC",
                                  "#248E84",
                                  "#F2583F",
                                  "#96503F")) +
    ggtitle("Corruption and Human development")
pc3
```
