---
title: "Stat535 Homework 2 -- Due Friday, September 22, 2017 before class through email anna@math.umass.edu"
name: Jie Wang
output: pdf_document
---
1. The data set rnf6080.dat records hourly rainfall at a certain location in Canada, every day from 1960 to 1980.
    a. First, we need to load the data set into R using the command 'read.table()'. Use the help function to learn what arguments this function takes. Once you have the necessary input, load the data set into R and make it a data frame called 'rain.df'.
Answer:
```{r}
rain.df <- read.table("http://www.math.umass.edu/~anna/Stat535Fall2017/rnf6080.dat")
```
 
    b. How many rows and columns does `rain.df` have? (If there are not 5070 rows and 27 columns, something is wrong; check the previous part to see what might have gone wrong in the previous part.)
Answer:  
```{r}
dim(rain.df)
```
    c. What are the names of the columns of `rain.df`?
Answer:
```{r}
colnames(rain.df)
```
    d. What is the value of row 5, column 7 of `rain.df`?
Answer:
```{r}
rain.df[5,7]
```
    e. Display the second row of `rain.df` in its entirety.
Answer:
```{r}
rain.df[2,]
```
    f. Explain what this command does:
```{r}
names(rain.df) <- c("year","month","day",seq(0,23))
```
by running it on your data and examining the object. (You may find the display functions `head()` and `tail()` useful here.) Is it clear now what the last 24 columns represent?

Answer: The command here renames the name of the each column. The last 24 columns represent 24 hourly rainfalls in chronological order during that day.


    g. Create a new column in the data frame called `daily`, which is the sum of the rightmost 24 columns. With this column, create a histogram of the values in this column, which are supposed to be daily rainfall values. What is wrong with this picture?  
Answer:
```{r}
rain.df$daily <- rowSums(rain.df[,4:27])
hist(rain.df$daily)
```
From the picture, we can find that for some dates, the daily rainfalls are negative values. This is not reasonable.


    h. Create a new data frame `rain.df.fixed` that takes the original and fixes it for the apparent flaw you have discovered. Having done this, produce a new histogram with the corrected data and explain why this is more reasonable.
    
Answer: here I removes the data points that have negative daily rainfall values and creates a new dataset `rain.df.fixed`. In this new dataset, all the daily rainfalls are nonnegative values.
```{r}
rain.df.fixed <- rain.df[ which(rain.df$daily >= 0), ]
#dim(rain.df.fixed)
hist(rain.df.fixed$daily)
```


2. Syntax and class-typing.
a. For each of the following commands, either explain why they should be errors, or explain the non-erroneous result.

```{r}
vector1 <- c("5", "12", "7", "32")
typeof(vector1)
max(vector1)
sort(vector1)
sum(vector1)
```
Answer: `vector1` is character vector. Each element of it is a character string. Therefore,`max` and `sort` functions follow the rules of sorting charcter variables. They will sort the elements by comparing the first character in the element firstly. If two elements have the same first character, they will compare them by consider the second characters of them. However, you cannot use `sum` function since `sum` function is only for numeric variables.


b. For the next series of commands, either explain their results, or why they should produce errors.

```{r}
vector2 <- c("5",7,12)
vector2[2] + vector2[3]
```
Answer: `c()` is a generic function which combines its arguments. All arguments are coerced to a common type. The output type  is determined from the highest type of the components in the hierarchy NULL < raw < logical < integer < real < complex < character < list < expression. Here, the output type of `vector2` is character since the type of the component `''5''` is charcter whic is > than type of `7` and `12`.

```{r}
dataframe3 <- data.frame(z1="5",z2=7,z3=12)
dataframe3[1,2] + dataframe3[1,3]
```
Answer: In dataframe, rows are for cases and  columns are for variables. Columns can have different types. Here,  `dataframe3[1,2]=7` and `dataframe3[1,3]=12` are numeric. Thus, we can do summation over these two terms.

```{r}
list4 <- list(z1="6", z2=42, z3="49", z4=126)
list4[[2]]+list4[[4]]
list4[2]+list4[4]
```
Answer: [ ] returns a subset of the list, which in itself will be a list. Therefore, we cannot do summation over `list4[2]` and `list4[4]`. [[ ]] drops names and structures and  returns just a single element from the list. Here
`list4[[2]]=42` and `list4[[4]]=126` are numeric. Therefore, we can do summation over them.

3. Working with functions and operators.
    a. The colon operator will create a sequence of integers in order. It is a special case of the function `seq()` which you saw earlier in this assignment. Using the help command `?seq` to learn about the function, design an expression that will give you the sequence of numbers from 1 to 10000 in increments of 372. Design another that will give you a sequence between 1 and 10000 that is exactly 50 numbers in length.
Answer:
```{r}
seq(1, 10000, by=372)
seq(1, 10000, length=50)
```
    b. The function `rep()` repeats a vector some number of times. Explain the difference between `rep(1:3, times=3)` and `rep(1:3, each=3)`.
Answer: `rep(1:3, times=3)` means repeat whole vector three times,i.e. creates a vector containing 3 copies of the original vector. `rep(1:3, each=3)` means each element of x is repeated 3 times, i.e. creates a vector containing 3 copies of  each element of  the original vector.