---
title: "Homework3 for STAT535"
author: "Jie Wang"
date: "September 29, 2017"
output:
  html_document: default
  pdf_document: default
---

1.
```{r}
library(stringr)
nhl1415 <- readLines("http://www.stat.cmu.edu/~cshalizi/statcomp/14/hw/03/NHLHockeySchedule2.html")
#which(nchar(nhl1415)==max((nchar(nhl1415))))
```
a. How many lines does it contain?
```{r}
length(nhl1415)
```
b. What is the total number of characters in the file?
```{r}
sum(nchar(nhl1415))
```
c. What is the maximun number of characters in a line?
```{r}
max((nchar(nhl1415)))
```
2. Answer: The first game is Montreal versus Toronto. The final game is Edmonton versus Vancouver.

3. Answer: The number of line corresponding to game 1 is 
```{r}
grep("Wed Oct 8, 2014.*Montreal",nhl1415)
```
The number of line corresponding to game 1230 is
```{r}
grep("Sat Apr 11, 2015.*Edmonton",nhl1415)
```
 The line corresponding to game 1  begins `</h3>`. The rest of them begin with with `</td>`.
 
4. Answer: For most URL for purchasing tickets, the link has home team in it.
5. Answer:
```{r}
gamerows=grep('class="skedStartDateSite">(.*?)</div>',nhl1415)
length(gamerows)
```
6. Answer:
```{r}
Dates=str_match(nhl1415[gamerows],'class="skedStartDateSite">(.*?)</div>')
date=Dates[,2]
date[1:10]
```
7. Answer:
Away team:
```{r}
away.pattern='Away.*javascript:void\\(0\\);">(.*?)</a>.*?Home'
away.team=str_match(nhl1415[gamerows],away.pattern)
away=away.team[,2]
away[1:10]
```
Home team:
```{r}
Home.pattern='Home.*javascript:void\\(0\\);">(.*?)</a>.*?Time'
Home.team=str_match(nhl1415[gamerows],Home.pattern)
Home=Home.team[,2]
Home[1:10]
```
8. Answer: 
```{r}
time.pattern='skedStartTimeEST">(.*?)</div>'
game.time=str_match(nhl1415[gamerows],time.pattern)
Time=game.time[,2]
Time[1:10]
```
9.
Answer: I am a little confused with this problem. In part 4, it mentions that the goal is to extract the URL for buying ticket. However, the URL for the **TICKET>** button is not for purchasing tickets. Actully, the **BUY/SELL** button is for buying tickets. In this question, I identify these two URL because I am not sure which the right one is.

The URL for the **TICKET>** button:
```{r}
URLgamerows=c(gamerows[2:1230], gamerows[1230]+2)
URL.pattern1='href=\"(.*?)"><span>TICKETS'
URL1=str_match(nhl1415[URLgamerows],URL.pattern1)
T.URL=URL1[,2]
length(T.URL)
T.URL[1:5]
```
The URL for purchasing ticket should be the **BUY/SELL** button:
```{r}
URL.pattern2='TICKETS›</span></a><a class="btn" shape="rect" href=\"(.*)"><span>BUY/SELL'
URL2=str_match(nhl1415[URLgamerows],URL.pattern2)
B.URL=URL2[,2]
length(B.URL)
B.URL[1:5]
```
For the URL for purchasing ticket button, most links have the home team in it.

10.Answer:
```{r}
df=data.frame(date, away, Home, Time, B.URL)
df[1221:1230,]
```

