---
title: "Stat535_HW5"
author: "Jie Wang"
date: "October 29, 2017"
output:
  pdf_document: default
  html_document: default
---

### 1.
```{r}
rm(list=ls())
library(RSQLite)
library(dplyr)
library(DBI)
```

### 2.	
#### a.
```{r}
con <- dbConnect(RSQLite::SQLite(), dbname='baseball.db')
dbListTables(con)
```
#### b.	
```{r}
payroll <- dbReadTable(con, "Salaries")
payroll %>%
  dplyr::filter(yearID == 2010) %>%
  group_by(teamID) %>%
  summarise(payroll = sum(salary)) %>%
  arrange(desc(payroll)) %>%
  head(n = 5)
#payroll2010 <- subset(payroll, yearID == 2010)
#payroll2010S <- cbind(aggregate(salary ~ teamID, payroll2010, sum))
#payroll2010S$teamID[payroll2010S$salary == max(payroll2010S$salary)]
```
#### c.	
```{r}
dbGetQuery(con, "
                 SELECT teamID, sum(salary) AS payroll
                 FROM Salaries
                 WHERE yearID == 2010
                 GROUP BY teamID
                 ORDER BY payroll DESC
                 LIMIT 5;
                 ")
```
#### d.	
```{r}
team_payroll <- dbGetQuery(con, "
                 SELECT yearID, teamID, sum(salary) AS payroll
                 FROM Salaries
                 WHERE yearID BETWEEN 1985 and 2010
                 GROUP BY teamID, yearID
                 ORDER BY payroll DESC;")
head(team_payroll, n = 10)
```

### 3.	

#### a.
```{r}
library(fImport)
library(timeDate)
library(timeSeries)
library(lubridate)
cpi <- read.table("CPIAUCSL.txt", head=T, skip=54)
cpi$DATE <- ymd(cpi$DATE)
cpi <- subset(cpi,months(DATE)=="January" & DATE <= ymd("2011-01-01") & DATE >= ymd("1985-01-01"))
cpi <- cpi[,2]
cpi <- cpi/cpi[length(cpi)]
year <- 1985:2011
plot(year,cpi)
```

#### b.	Calculate the inflation-adjusted payroll of each baseball team over time.  (Hint:  You may find plyr helpful here.)
```{r}
#convert_to_2011 <- function(amt, yr) {
#  y <- amt / cpi[yr - 1985 + 1]
#}
#convert_to_2011(payroll, yearID))
team_payroll <- team_payroll %>%
  mutate(adj_payroll = payroll/cpi[yearID-1985+1])
head(team_payroll, n=10)
```
#### c.	
```{r}
library(ggplot2)
ggplot(team_payroll,
       aes(x = yearID,
           y = adj_payroll,
           color = teamID)) + 
  geom_line() +
  theme_bw() +
  labs(x = "Year",
       y = "Adjusted Payroll")
```

 
#### d.	
```{r}
library(ggplot2)
ggplot(team_payroll,
       aes(x = yearID,
           y = log(adj_payroll),
           color = teamID)) + 
  geom_line() +
  theme_bw() +
  labs(x = "Year",
       y = "Log of Adjusted Payroll")
```
#### e.	
```{r}
slopes <- team_payroll %>% group_by(teamID) %>%   mutate(slopes=coef(lm(log(adj_payroll)~yearID))[2]) 

boxplot(slopes$slopes)

team_payroll %>% group_by(yearID)  %>%  top_n(n = 5, wt = adj_payroll) %>% arrange(desc(yearID)) %>% group_by(teamID) %>% count() %>% arrange(desc(n))

team_payroll %>% group_by(yearID) %>% summarise(max=max(adj_payroll), min=min(adj_payroll)) %>% 
  mutate(factor=max/min) %>% ggplot(aes(x=yearID, y=factor)) +
  geom_line()
```
From the result, we can see that in general, the payrolls fell behind the inflation.
Also we can see from the  pictures in Q3, there is no team whose payrolls have consistently been higher than the others.
The gap between the highest and the lowest payrolls has grown. 

### 4.	
```{r}
teams <- dbGetQuery(con, "select yearID, teamID, W, G from Teams")
team_payroll %>% inner_join(teams) %>% mutate(win_prop=W/G)%>%
  ggplot(aes(x=win_prop, y=adj_payroll))+geom_point()+geom_smooth(method="lm")
```

### 5.	
```{r}
salary_class_df <- payroll %>% dplyr::group_by(playerID) %>% 
  summarise(mean.salary = mean(salary, na.rm=T)) %>%
  mutate(salary_class = cut(mean.salary, breaks=c(0, 50000, 100000, 150000, 200000, max(mean.salary)), labels=as.character(1:5)))
head(salary_class_df, n = 15)

library(sqldf)
salary_class_df1 <- dbGetQuery(con,"select playerID,avg(salary) as mean_salary from Salaries group by playerID")
salary_class_df2 <- sqldf::sqldf("select playerID,mean_salary,min(5,floor(mean_salary/5000)) as salary_class from salary_class_df1")
head(salary_class_df2, n = 15)
```

